Supporting Information : Asymmetric tail-dependence in extreme climatic events affects population-extinction risk

### 2019-10-10 SuppMat.Rmd
code edited to get common kendall's tau

```{r sim_linear_mtd, echo=F,  cache=T, cache.extra=list(seed,mtime("ext_risk_cop_age_str.R"))}
# extinction risk with moderate tail dep. for single patch linear age structure model

@@

numsims<-10000
numsteps<-25
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-Inf
ktau<-0.6  # kendall's tau

@@

```{r sim_nonlinear_mtd, echo=F,  cache=T, cache.extra=list(seed,mtime("ext_risk_cop_age_str.R"))}
# extinction risk with moderate tail dep. for single patch non-linear age structure model

@@

numsims<-10000
numsteps<-25
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-100
ktau<-0.6  # kendall's tau

@@

```{r sim_ricker_scl_1, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ext_thrs<-K/10
model<-"ricker"

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_hassell_scl_1, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_msmith_scl_0.8, echo=F, cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"msmith"
scl<-0.8

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_pennycuick_scl_1, echo=F, cache=T, cache.extra=list(seed,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"pennycuick"
scl<-1

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_verhulst_scl_0.6, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"verhulst"
scl<-0.6

@@

    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_abrewer_scl_0.6, echo=F,  cache=T, cache.extra=list(seed,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"austinbrewer"
scl<-0.6

>>>>

```{r get_ktau_common, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("ExtremeTailDep.R"))}
set.seed(seed)
library(copula)
source("./ExtremeTailDep.R")

np<-100000

#for(i in 1:5){ # for loop to ensure the consistency of Kendall's tau with specified np
  xtc_r<-retd(n=np,d=2,rl=1,mn=0,sdev=1) # copula with extreme right tail

  start_time <- Sys.time()
  ktau_common<- cor(xtc_r[,1],xtc_r[,2],method="kendall") #get the kendall's tau
  end_time <- Sys.time()

#  cat("points = ",np, ", ktau_common = ", ktau_common, ", run time = ", (end_time -start_time),"\n")
#}

# see the change in 3rd decimal place
#points =  1e+05 , ktau_common =  0.7512526 , run time =  1.837576 
#points =  1e+05 , ktau_common =  0.7507594 , run time =  1.864947 
#points =  1e+05 , ktau_common =  0.7497681 , run time =  1.862879 
#points =  1e+05 , ktau_common =  0.7487744 , run time =  1.854317 
#points =  1e+05 , ktau_common =  0.7516491 , run time =  1.840355

#--------- Plot for intro + methods ------------------------------------

# flip xtc_r to get xtc_l
#xtc_l<-1-xtc_r

# make marginals uniform 
xtc_r<-pnorm(xtc_r)
xtc_l<-1-xtc_r

# for clayton : left tail dep.
copC<-claytonCopula(3)
parC<-iTau(copC,tau=ktau_common)

# first generate Clayton copula 
cc<-claytonCopula(par=parC,dim=2)
mtc_l<-rCopula(np,cc)

# flip Clayton copula 
mtc_r<-1-mtc_l

pdf("./Results/fig_4_copula.pdf", height=3, width=12)
op<-par(mfrow=c(1,4),mar=c(4,4,2,2),mgp=c(2,1,0))

# extreme left tail
plot(xtc_l[,1],xtc_l[,2],col=rgb(0,0,0,0.05),pch=19,xlab="u",ylab="v",cex.lab=2)
legend(x="topleft",legend="A",bty="n",cex=2)

# moderate left tail
plot(mtc_l[,1],mtc_l[,2],col=rgb(0,0,0,0.05),pch=19,xlab="u",ylab="v",cex.lab=2)
legend(x="topleft",legend="B",bty="n",cex=2)

# moderate right tail
plot(mtc_r[,1],mtc_r[,2],col=rgb(0,0,0,0.05),pch=19,xlab="u",ylab="v",cex.lab=2)
legend(x="topleft",legend="C",bty="n",cex=2)

# extreme right tail
plot(xtc_r[,1],xtc_r[,2],col=rgb(0,0,0,0.05),pch=19,xlab="u",ylab="v",cex.lab=2)
legend(x="topleft",legend="D",bty="n",cex=2)

```{r sim_linear_mtd, echo=F,  cache=T, cache.extra=list(seed,ktau_common,mtime("ext_risk_cop_age_str.R"))}
# extinction risk with moderate tail dep. for single patch linear age structure model

@@

numsims<-10000
numsteps<-25
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-Inf
ktau<-ktau_common  # kendall's tau

@@

```{r sim_nonlinear_mtd, echo=F,  cache=T, cache.extra=list(seed,ktau_common,mtime("ext_risk_cop_age_str.R"))}
# extinction risk with moderate tail dep. for single patch non-linear age structure model

@@

numsims<-10000
numsteps<-25
p0<-c(5,10)
ext_thrs<-2
gshape<-2
gscale<-1
bshape1<-3
bshape2<-2
par_dist<-c(gshape,gscale,bshape1,bshape2)
omg<-100
ktau<-ktau_common  # kendall's tau

@@

```{r sim_ricker_scl_1, echo=F,  cache=T, cache.extra=list(seed,ktau_common,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

numsims<-10000
numsteps<-25
numlocs<-5
K<-50
scl<-1
ktau<-ktau_common
ext_thrs<-K/10
model<-"ricker"

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_hassell_scl_1, echo=F,  cache=T, cache.extra=list(seed,ktau_common,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

@@

numsims<-10000
numsteps<-25
numlocs<-5
a<-0.5
b<-100
scl<-1
ktau<-ktau_common

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_msmith_scl_0.8, echo=F, cache=T, cache.extra=list(seed,ktau_common,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"msmith"
scl<-0.8
ktau<-ktau_common

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_pennycuick_scl_1, echo=F, cache=T, cache.extra=list(seed,ktau_common,a_pennycuick,b_pennycuick,rc_pennycuick,r_bf_pennycuick,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"pennycuick"
scl<-1
ktau<-ktau_common

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_verhulst_scl_0.6, echo=F,  cache=T, cache.extra=list(seed,ktau_common,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"verhulst"
scl<-0.6
ktau<-ktau_common

@@

    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

@@

    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,ktau=ktau,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

@@

```{r sim_abrewer_scl_0.6, echo=F,  cache=T, cache.extra=list(seed,ktau_common,mtime("mydispersal.R"),mtime("ExtremeTailDep.R"))}
set.seed(seed)
source("mydispersal.R")

model<-"austinbrewer"
scl<-0.6
ktau<-ktau_common
